---
title: "combine_repeated_entries"
author: "Andre M Chagas"
date: "16/07/2020"
output: html_document
---
## RMarkdown to filter and combine repetitive entries of the 'allData.csv' file

```{r attach-libraries}

## clear workspace
rm(list = ls())

library(tidyverse)#
library(here)
```
```



```{r load-csv}

allData <- read.csv(here("data","allData.csv"))


names(allData)

## allData$ENTRYTYPE
##"title" contain the entries we need

```

```{r sort-title}

## set all titles to lower case
lowTitles<-tolower(allData$title)

##order titles
ordered<-order(lowTitles)

##show first 10 entries
head(lowTitles[ordered],10)

## save to file to cross-check
write.csv(lowTitles[ordered],here("data","lowTitles_first.csv"))

```


### from this first check, we can see that the titles need some cleaning:

- some entries are with a single quote, some with double, and some with tilted quote
- some have \"
- some entries have a newline escape in the middle.
- there are mixes between hyphens (-) and dashes(--)
- etc

So let's clean it by:

- making all ' and ` and `` and \" into a single '
- removing the newline escape
- etc


```{r clean-naming}

## remove \n
lowTitles <- gsub("\n"," ",lowTitles)



## remove "\\&"
lowTitles <- gsub(" \\&"," and",lowTitles)
lowTitles <- gsub("\\&","and",lowTitles)

## substitute " `" for '
lowTitles <- gsub(" `","'",lowTitles)

## substitute "` " for '
lowTitles <- gsub("` ","'",lowTitles)

## substitute "`" for '
lowTitles <- gsub("`","'",lowTitles)

## substitute "''" for '
lowTitles <- gsub("''","'",lowTitles)

## substitute "–" for "-"
lowTitles <- gsub("–","-",lowTitles)
lowTitles <- gsub("—","-",lowTitles)


## substitute " :" for ":"
lowTitles <- gsub(" :",":",lowTitles)

## substitute " - " for "-"
lowTitles <- gsub(" - ","-",lowTitles)

## substitute "- " for "-"
lowTitles <- gsub("- ","-",lowTitles)

## substitute "µ" for "um"
lowTitles <- gsub("µ","um",lowTitles)

## substitute "®" for "(r)"
lowTitles <- gsub("®","(r)",lowTitles)

## substitute " ? " for "? "
lowTitles <- gsub(" \\? ","\\? ",lowTitles)

## "rapi morphological exploration with the poppy humanoid platform." 
## "rapi morphological exploration with the poppy humanoid platform"
## "rosmotic: a scalable smart home for blind people controlled with an app."  
## "rosmotic: a scalable smart home for blind people controlled with an app"  
lowTitles <- gsub("\\.","",lowTitles)

## substitute "&" for "and"
#lowTitles <- gsub("&","and",lowTitles)

## substitute """ for '
#lowTitles <- gsub("\"","'",lowTitles)

## remove \"
lowTitles <- gsub("\"","",lowTitles)

## some entries are duplicated due to typos

## "a dataglove hardware design and real-time sign gesture interpretation"                                                                              ## "a dataglove hardware design and real-time sign gesture interpretation." 
lowTitles <- gsub("interpretation.","interpretation",lowTitles) 


## "a human-computer interface based on the “voluntary” pupil accommodative response"                                                                   ## "a human-computer interface based on the'voluntary' pupil accommodative response"  
lowTitles <- gsub("'voluntary'"," “voluntary”",lowTitles) 

## "a low-cost exp-golomb hardware architecture for h.264/avc entropy coder"                                                                         
## "a low-cost exp\\_golomb hardware architecture for h.264/avc entropy coder"
lowTitles <- gsub("p\\_g","p-g",lowTitles) 

## "a low-cost iot based environmental monitoring system. a citizen approach to pollution awareness"                                                    ## "a low-cost iot based environmental monitoring system. a citizen approach to pollution awareness."  
lowTitles <- gsub("awareness.","awareness",lowTitles)

## "a low-cost open source hardware in control education. case study: arduino-feedback ms-150"                                                          ## "a low-cost open source hardware in control education. case study:arduino-feedback ms-150"  
lowTitles <- gsub("study:arduino","study: arduino",lowTitles)

## "a low-cost platform for eye-tracking research: using pupil (c) in behavior analysis"                                                                ## "a low-cost platform for eye-tracking research: using pupil© in behavior analysis"
lowTitles <- gsub("©","(c)",lowTitles)

## "a modular path planning solution for wire + arc additive manufacturing"                                
## "a modular path planning solution for wire plus arc additive manufacturing" 
lowTitles <- gsub(" + "," plus ",lowTitles)

##  "a new paradigm for open robotics research and education with the c plus plus ooml"                                                                  ## "a new paradigm for open robotics research and education with the c++ ooml"   
lowTitles <- gsub(" plus plus","++",lowTitles)

## "a real-time imaging system fo lumber strength prediction"                                                                                           ## "a real-time imaging system for lumber strength prediction"    
lowTitles <- gsub("system fo lumber","system for lumber",lowTitles)

## "a review of arduino board's, lilypad's \\and arduino shields"                                                                                       ## "a review of arduino board's, lilypad's and arduino shields"  

## "a simple strategy for carboxylated mwnts as a metal-free electrosensor for anchoring the rhb c=n group"                                             ## "a simple strategy for carboxylated mwnts as a metal-free electrosensor for anchoring the rhb cn group" 
lowTitles <- gsub("rhb c=n","rhb cn",lowTitles)


## "afm nanœye – development of an education oriented high resolution profilometer"                                                                      ## "afm nanoeye-development of an education oriented high resolution profilometer"  
lowTitles <- gsub("œ","oe",lowTitles)

## "an easily deployable system for indoor positioining using wi-fi network"                                                                            ## "an easily deployable system for indoor positioning using wi-fi network" 
lowTitles <- gsub("positioining","positioning",lowTitles)

## "an efficient estimator for target localization in a multi-station redundancy system without matrix inversion"                                        ## "an efficient estimator for target localization in a multistation redundancy system without matrix inversion" 
lowTitles <- gsub("multi-station","multistation",lowTitles)

## "an energy aware end-to-end trust mechanism for iot healthcare applications"                                                                         ## "an energy aware end-to-end trust mechanism for iot healthcare applications."  
#lowTitles <- gsub("applications.","applications",lowTitles)

## "an iot based service system as a research and educational platfor"                                                                                  ## "an iot based service system as a research and educational platform"  
lowTitles <- gsub("and educational platfor","and educational platform",lowTitles)

## "cost-effective n:1 firewall array via subnet-levcl load balancing by sdn/openflow switches"                               
## "cost-effective n:1 firewall array via subnet-level load balancing by sdn/openflow switches"  
## substitute "levcl" for "level"
lowTitles <- gsub("levcl","level",lowTitles)

## "cap floor - a flexible capacitive indoor localization system"                                                                    
## "capfloor - a flexible capacitive indoor localization system" 
## substitute "cap floor" for "capfloor"
lowTitles <- gsub("cap floor","capfloor",lowTitles)

## "detection of episodes of major depression in older adults through physiological markers and movement patterns case study"                    
## "detection of episodes of major depression in older adults through physiological markers and movement patterns: case study" 
# substitute "movement patterns:" for "movement patterns"
lowTitles <- gsub("movement patterns:","movement patterns",lowTitles)



## "deploying sdn in geant production network"                                                                                                          ## "deploying sdn in géant production network" 

## "development of the gambiarradio educacional prototype: device for transmitting audio via fm radio waves based on raspberry pi"            
## "development of the gambiarrádio educational prototype: device for transmitting audio via fm radio waves based on raspberry pi"
lowTitles <- gsub("á","a",lowTitles)
lowTitles <- gsub("ó","o",lowTitles)
lowTitles <- gsub("é","e",lowTitles)

## "differentiation between organic and non-organic apples using diffraction grating and image processing—a cost-effective approach"                    ## "differentiation between organic and non-organic apples using diffraction grating and image processinga cost-effective approach"   
lowTitles <- gsub("processing—a","processinga",lowTitles)

## "bridging digital divide: 'village wireless lan', a low cost network infrastructure solution for digital communication, information dissemination and education in rural bangladesh"                                
## "bridging digital divide:'village wireless lan', a low cost network infrastructure solution for digital communication, information dissemination \\and education in rural bangladesh"
lowTitles <- gsub("divide:'village","divide: 'village",lowTitles)


## "bipolar transistor application for «on-line» neutron fluence registration"                                                                       
## "bipolar transistor application for'on-line' neutron fluence registration"  
lowTitles <- gsub(" «on-line»","'on-line'",lowTitles)

## "implementation of vision-based autonomous mobile platform to control by a* algorithm"                                                                
## "implementation of vision-based autonomous mobile platform to control by a∗ algorithm"
lowTitles <- gsub("∗","*",lowTitles)

## "lighting control actuator design and development for a zigbee network with a web server mounted on raspberry pi." 
## "lighting control actuator design and development for a zigbee network with a web server mounted on raspberry pi"
#lowTitles <- gsub("pi.","pi",lowTitles)

## "livecoding the synthkit: littlebits as an embodied programming language"
## "livecoding the synthkit: little bits as an embodied programming language"
lowTitles <- gsub("littlebits","little bits",lowTitles)

## "maker movement influence on students' learning motivation and learning achievement-a learning style perspective"                                    
## "maker movement influence on students' learning motivation and learning achievement-a learning style perspective"                                    
lowTitles <- gsub("’","'",lowTitles)

## "modular open hardware omnidirectional platform for mobile robot research *" 
## "modular open hardware omnidirectional platform for mobile robot research" 
lowTitles <- gsub(" \\*","",lowTitles)

## "open labware: 3-d printing your own lab equipment" 
## "open labware: 3-d printing your own lab equipment (vol 13, e1002086, 2015)"
lowTitles <- gsub(" (vol 13, e1002086, 2015)","",lowTitles)


## "opens hub: real-time data logging, connecting field sensors t o google sheets"
## "opens hub: real-time data logging, connecting field sensors t o google sheets"
lowTitles <- gsub(" t o "," to ",lowTitles)

## "progress on the self service kiosk for testing the uv protection on sunglasses-polynomial and neural network approximation for calculating light transmittance"
## "progress on the self-service kiosk for testing the uv protection on sunglasses-polynomial and neural network approximation for calculating light transmittance"   
lowTitles <- gsub("self service","self-service",lowTitles)




## "retrofit of air conditioning systems through an wireless sensor and actuator network: an iot-based application for smart buildings"  
## "retrofit of air conditioning systems through an wireless sensor and actuator network an iot-based application for smart buildings" 
lowTitles <- gsub("network an","network: an",lowTitles)

## "self-sustainable monitoring station for f,xtreme environments (s3me2): design and validation" 
## "self-sustainable monitoring station for extreme environments (s3me2): design and validation" 
lowTitles <- gsub("f,xtreme","extreme",lowTitles)

## "simultaneous determination of vitamin b-1 and b-2 in complex cereal foods, by reverse phase isocratic hplc-uv" 
## "simultaneous determination of vitamin b 1 and b 2 in complex cereal foods, by reverse phase isocratic hplc-uv" 
lowTitles <- gsub("vitamin b 1 and b 2","vitamin b-1 and b-2",lowTitles)

## "sniffi: a portable development gas sensing embedded system" 
## "sniffi a portable development gas sensing embedded system" 
lowTitles <- gsub("sniffi:","sniffi",lowTitles)

## systems overview of ono: a diy reproducible open source social robot
## systems overview of ono a diy reproducible open source social robot
lowTitles <- gsub("ono:","ono",lowTitles)

## "the complementarity of openness: how makerbot leveraged thingiverse in 3dprinting"    
## "the complementarity of openness: how makerbot leveraged thingiverse in 3d printing"    
lowTitles <- gsub("3dprinting","3d printing",lowTitles)

## "the emergence of open construction systems: a sustainable paradigm in the construction sector?" 
## "the emergence of open construction systems: a sustainable paradigm in the construction sector" 
lowTitles <- gsub("sector?","sector",lowTitles)

## "towards secure elements for trusted transactions in blockchain and blochchain iot (biot) platforms. invited paper"   
## "towards secure elements for trusted transactions in blockchain and blochchain iot (biot) platforms"
lowTitles <- gsub(" invited paper","",lowTitles)

## "very high resolution crop surface models (csms) from uav-based stereo images for rice growth monitoring in northeast china" 
## "very high resolution crop surface models (csm) from uav-based stereo images for rice growth monitoring in northeast china" 
lowTitles <- gsub("csms","csm",lowTitles)

## "x4-mag: a low-cost open-source micro-quadrotor and its linux based controller" 
## "x4-mag: a low-cost open-source micro-quadrotor and its linux-based controller" 
lowTitles <- gsub("linux-based","linux based",lowTitles)

#### brought this one below on myself
## "openwsn \\and openmote: demo'ing a complete ecosystem for the industrial internet of things"
## "openwsn and openmote: demo'ing a complete ecosystem for the industrial internet of things"

## CHECK THESE ONES BELOW in MORE DETAIL BEFORE MERGE

## "research on detection of beef freshness parameters based on multi spectral diffuse reflectance method [基于多光谱漫反射的牛肉品质参数检测方法研究]" 
## "research on detection of beef freshness parameters based on multi spectral diffuse reflectance method"

## "optimization and hardware implementation of image watermarking for low cost applications" 
## "optimization and hardware implementation of image and video watermarking for low-cost applications" 

## "peristaltic pump and detection system controlled by an arduino open source hardware developed and designed for application in a flow analysis system"
## "peristaltic pump and detection system controlled by an arduino open source hardware developed and designed for application in a flow analysis system [construção de uma bomba peristaltica e de um sistema de detecção utilizando um hardware de codigo fonte aberto ⇜arduino⇝ para analise em fluxo]"

## "archeorobotics. open robotic applications and extreme archeology"                                                                                   ## "archeorobotics. open robotic applications and extreme archeology [archeorobotics. applicazioni robotiche aperte e archeologia estrema]" 


## "arduino microcontroller processing for everyone! third edition barrett"                                                                              
## "arduino microcontroller: processing for everyone"    

## "beach profiles: should the emery rod method be discarded?"                                                                                          ## "beach profiles: should the emery rod method be discarded? [perfis de praia: deve o método das balizas de emery ser abandonado?]"  

# "big data in chemicals sector"                                                                                                                 
# "big data in the chemicals sector" 


## "designing low-cost hardware accelerators for ce devices"                                                           
## "designing low-cost hardware accelerators for ce devices [hardware matters]"   

## "design of an open source-based control platform for an underwater remotely operated vehicle"                                                         
## "design of an open source-based control platform for an underwater remotely operated vehicle [diseño de una plataforma de control basada en fuente abierta para un vehículo subacuático operado remotamente]"  

## "design and implementation of a modern automatic deformation monitoring system"                                                            
## "design and implementation of a modern automatic deformation monitoring system: towards an open source software platform for geodetical and geotechnical measurements" 

## "consideration of the versatility of the open prototype for educational nanosats cubesat design"                                                   
## "consideration of the versatility of the open prototype for educational nanosats cubesat design an overview of multiple uses and discussion of prospective future uses"  

## "a compact hardware implementation of sm3"                                                                                                           ## "a compact hardware implementation of sm3 hash function"  

## "3d cardiac electrical activity model"                                                                                                               ## "3d cardiac electrical activity model [3d model električne aktivnosti srca]"    

## "learning basic robotics and val ii programming with lego mindstorms robots"                                                                         ## "learning basic robotics and val ii programming with lego mindstorms robots [aprendizaje de robótica básica y programación en val ii usando robots lego mindstoms]"   

 


## reorder things 
ordered<-order(lowTitles)


head(lowTitles[ordered],10)


## subsitute title with the lower case titles
allData[,"title"]<-lowTitles

#reorder allData according to sorted titles
allData<-allData[ordered,]

head(allData$title)




```


```{r check-duplicates}


## number of non-repeated entries
length(allData$title)-length(unique(allData$title))

## de 
test<-(unique(allData$title))
## save entries that are unique for a quick human check
write.csv(test,here("data","quickCheck.csv"))

## get all duplicated titles
rep_titles<-allData[duplicated(allData$title) ,"title"]


```


```{r combine-duplicates}




length(all_data[rep_titles[1],])




```


